Lexical Richness as a Lens: Exploring the Influence of Social Class on Authors' Writings

### 2024-03-16 paper/paper.qmd
data: average table

ggplot(cttr_all, aes(x = title, y = word_count, color = author)) +
  geom_line(linewidth=1) +
  labs(x = "Title",
       y = "Word Count") +
  theme(panel.background = element_rect(fill = "white"),
              panel.grid.major = element_line(colour = "grey"),
              plot.title = element_text(color = "black", size = 14, face = "bold"),
              axis.title = element_text(color = "black"))
```
# TODO: Explain

>>>>

word_distribution <- read.csv(here::here("data/analysis_data/wordcount_dist.csv"))

word_distribution |>
  select(author, average, stddev) |>
  kable(
    col.names = c("author", "word count mean", "word count std. dev."),
    digits = 2,
    booktabs = TRUE
  )
```
# TODO: Explain
